---
title: "Activity 4: Regular Expressions"
editor: source
---

# Activity: Regular Expression Sleuthing


First, load the lyrics from class:

```{r}
lyrics <- c("But I would walk 500 miles",
            "Yeah, 360. When you're in the mirror, do you like what you see?", 
            "I have loved you for a 1000 years, I'll love you for a 1000 more",
            "Where 2 and 2 always makes a 5",
            "17-38, ay",
            "I'm so 3008, You so 2000 and late")
```


## Regular Expressions

What does `{n}` do?

```{r}
str_view_all(lyrics, "[:digit:]{2}")
```

ANSWER:

------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:alnum:]")
```

ANSWER:

------------------------------------------------------------------------

## Quantifiers: What does each of these do?

Fill out what each of the quantifiers below does. Use the below code chunk to try them out. I got you started by doing 2 of them for you.

ANSWER:

-   `?`: 0 or 1
-   `*`:
-   `+`: 1 or more
-   `{n}`:
-   `{n,}`:
-   `{n,m}`:

```{r}
str_view_all(lyrics, "[:alnum:]{4,}")
```

------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:alpha:]")
```

ANSWER:

------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:upper:]")
```

ANSWER:

------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:punct:]")
```

ANSWER:

------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:graph:]")
```

ANSWER:

------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:space:]")
```

ANSWER:

------------------------------------------------------------------------

## Character Classes

-   Can also create your own.

-   What pattern does this regexp match?

-   why no colons on this one?

```{r}
str_view_all(lyrics, "[aeiou]")
```

ANSWER:

------------------------------------------------------------------------

## Other Handy Regexps

-   What pattern does this regexp match?

-   Why do we need an extra `\`?

```{r}
str_view_all(lyrics, "\\d")
```

ANSWER:

------------------------------------------------------------------------

## Other Handy Regexps

-   What pattern does this regexp match?

```{r}
str_view_all(lyrics, "\\W")
```

ANSWER:

------------------------------------------------------------------------

## Other Handy Regexps

-   What pattern does this regexp match?

```{r}
str_view_all(lyrics, "Whe[:alpha:]+")
```

ANSWER:

------------------------------------------------------------------------

## Groups

-   What pattern does this regexp match?

-   What do you think "\\1" is doing

```{r}
str_view_all(lyrics, "(\\d)\\1")
```

ANSWER:

------------------------------------------------------------------------

## Groups

-   What pattern does this regexp match?

-   Now, what do you think the "\\1" is doing? 

```{r}
str_view_all(lyrics, "(\\d)\\1\\1")
```

ANSWER:

------------------------------------------------------------------------

## Groups

-   What pattern does this regexp match?

```{r}
str_view_all(lyrics, "([:alnum:])(\\s)[:alnum:]+\\2\\1")
```

ANSWER:

------------------------------------------------------------------------

## Other Handy Regexps

-   What pattern does this regexp match?

```{r}
str_view_all(lyrics, "\\b")
```

ANSWER:

------------------------------------------------------------------------

## Anchors

-   What pattern does this regexp match?

-   What do you think the "^" is doing?

```{r}
str_view_all(lyrics, "^\\d+")
```

ANSWER:

------------------------------------------------------------------------

## Anchors

-   What pattern does this regexp match?

-   What do you think the "$" is doing?

```{r}
str_view_all(lyrics, "\\d+$")
```

ANSWER:

------------------------------------------------------------------------

## Alternates

-   What pattern does this regexp match?

-   What is the "^" doing now? Hint: It is different than before.

```{r}
str_view_all(lyrics, "[^aeiou]")
```

ANSWER:

------------------------------------------------------------------------

## Alternates

-   What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[0-2]0")
```

ANSWER:

------------------------------------------------------------------------

## Look Arounds

```{r}
str_view_all(lyrics, "(?<=\\d )[:alpha:]+")
```

ANSWER:

------------------------------------------------------------------------

## Look Arounds

```{r}
str_view_all(lyrics, "[:alpha:]+(?= \\d+)")
```

ANSWER:
