---
title: "Activity: Data Wrangling"
---

## Instructions

For this activity, work in groups of 2 - 3. Work together to come to a solution, and help each other out when stuck! The goal is to use the journey as a vessel for your and your peer's learning, not to make it to the 'correct' answer as fast as possible.

## Problem 0: load (and install) packages

```{r}
# Packages (I got you started)
library(tidyverse)
library(Lahman) # the baseball data
library(nycflights13) # the flights data
```

## Problem 1: Baseball

The Major League Baseball Angels have at times been called the California Angels (CAL), the Anaheim Angels (ANA), and the Los Angeles Angels of Anaheim (LAA). Using the `Teams` data frame in the `Lahman` package:

1.  Find the 10 most successful seasons in Angels history, defining “successful” as the fraction of regular-season games won in the year. In the table you create, include the `yearID`, `teamID`, `lgID`, `W`, `L`, and `WSWin`. See the documentation for `Teams` (see `help(Teams)`) for the definition of these variables.

2.  Have the Angels ever won the World Series? If so, when?

```{r}
data(Teams)
head(Teams)
```

## Problem 2: Flights

Use the `nycflights13` package and the `flights` data frame to answer the following questions:

1.  What plane (specified by the `tailnum` variable) traveled the most times from New York City airports in 2013?

2.  Plot the number of trips per week over the year.

```{r}
data(flights)
head(flights)
```
